Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-20 paper/paper.tex
updated figures

@@

\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{distributions}
    \caption[Percentage of high scores achieved by each algorithm on different ensemble types for all five applications.]{Percentage of high scores achieved by each algorithm on different ensemble types for all five applications. C = Constant ensembles, PS = Pareto Sorted ensembles, PU = Pareto Unsorted ensembles, US = Uniform Sorted ensembles, and UU = Uniform Unsorted ensembles.}
    \label{fig:distributions}
\end{figure*}

@@

Figure~\ref{fig:variances_scores} shows relative performance as a percentage of the number of high scores achieved by each algorithm as the error increases. The figure shows that, for this experiment, the scores remain the same as the error increases. This is a result of the way the error is applied. Since the error is selected uniformly from $-p\%$ to $+p\%$ it is equally likely that the error will be positive as negative. In other words, it is equally likely that a task will take longer as it is that the task will be shorter. Because the application used in this experiment, Montage, has a low task runtime variance, applying the error leaves the total runtime of the tasks in the workflow unchanged---the total number of CPU hours in each workflow remains the same regardless of the error. The end result is that the dynamic algorithms are able to achieve the same score without exceeding the constraints by using a different schedule that finishes the same total amount of work using the same budget and deadline. If we had applied a skewed error, for example, an error that was more likely to be positive than negative, then the scores for the dynamic algorithms would decrease relative to the static algorithm as the error increased.

@@

\begin{figure*}[p]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=\textwidth]{variances_budget}
    }\\
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=\textwidth]{variances_deadline}
    }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{variances_scores}
  \caption{Percentage of high scores achieved by each algorithm on Montage with uniform unsorted ensembles when runtime estimate error varies from $\pm$0\% to $\pm$50\%.}
  \label{fig:variances_scores}
\end{figure}

\begin{figure*}[p]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=\textwidth]{delays_budget}
    }\\
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=\textwidth]{delays_deadline}
    }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

Figure~\ref{fig:delays_scores} shows the relative performance as a percentage of the number of high scores achieved by each algorithm as the provisioning delay increases. This figure shows that, as the delay increases, the relative performance of the static algorithm increases as well. This behavior is a result of the fact that the static algorithm is, in essence, cheating by using more time and money than the dynamic algorithms. In the previous section we showed how the relative performance of the algorithms remains the same when a uniform error is applied to the runtime constraints. In that case, the dynamic algorithms adapted to the error by rearranging the schedule to accomplish the same amount of work given the same deadline and budget. In this case, the dynamic algorithms adapt by performing less work (executing fewer workflows) to remain within the constraints while accounting for the delays. In both cases, the static algorithm completed the same amount of work, but did so by exceeding the constraints.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{delays_scores}
  \caption{Percentage of high scores achieved by each algorithm on Montage with uniform unsorted ensembles when provisioning delay varies from 0 seconds to 15 minutes.}
  \label{fig:delays_scores}
\end{figure}

>>>>

\begin{figure}[htb]
    \centering
    \subfloat[size]{
        \includegraphics[width=0.75\columnwidth]{size-selected-LIGO}
        }\\
    \subfloat[cost]{
        \includegraphics[width=0.75\columnwidth]{cost-selectedLIGO}
        }
    \caption{Example performance of algorithms expressed in
    sum of dag sizes and effective cost, data for LIGO application, Pareto
    Sorted ensemble of 100 workflows.}
    \label{fig:size-cost}
\end{figure}

@@

\begin{figure*}[ht]
    \centering
    \includegraphics[width=0.75\textwidth]{run-finish-variations-test-0-output-distributions}
    \caption[Percentage of high scores achieved by each algorithm on different ensemble types for all five applications.]{Percentage of high scores achieved by each algorithm on different ensemble types for all five applications. C = Constant ensembles, PS = Pareto Sorted ensembles, PU = Pareto Unsorted ensembles, US = Uniform Sorted ensembles, and UU = Uniform Unsorted ensembles.}
    \label{fig:distributions}
\end{figure*}

@@

% Figure~\ref{fig:variances_scores} shows relative performance as a percentage of the number of high scores achieved by each algorithm as the error increases. The figure shows that, for this experiment, the scores remain the same as the error increases. This is a result of the way the error is applied. Since the error is selected uniformly from $-p\%$ to $+p\%$ it is equally likely that the error will be positive as negative. In other words, it is equally likely that a task will take longer as it is that the task will be shorter. Because the application used in this experiment, Montage, has a low task runtime variance, applying the error leaves the total runtime of the tasks in the workflow unchanged---the total number of CPU hours in each workflow remains the same regardless of the error. The end result is that the dynamic algorithms are able to achieve the same score without exceeding the constraints by using a different schedule that finishes the same total amount of work using the same budget and deadline. If we had applied a skewed error, for example, an error that was more likely to be positive than negative, then the scores for the dynamic algorithms would decrease relative to the static algorithm as the error increased.

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-variations-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-variations-test-0-output-makespan-all}
        }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

%\begin{figure}[ht]
%  \centering
%  \includegraphics[width=0.5\textwidth]{variances_scores}
%  \caption{Percentage of high scores achieved by each algorithm on Montage with
%  uniform unsorted ensembles when runtime estimate error varies from $\pm$0\%
%  to $\pm$50\%.}
%  \label{fig:variances_scores}
%\end{figure}

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-delays-test-0-output-cost-montage-uniform_unsorted}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-delays-test-0-output-dagfinish-montage-uniform_unsorted}
        }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

% Figure~\ref{fig:delays_scores} shows the relative performance as a percentage of the number of high scores achieved by each algorithm as the provisioning delay increases. This figure shows that, as the delay increases, the relative performance of the static algorithm increases as well. This behavior is a result of the fact that the static algorithm is, in essence, cheating by using more time and money than the dynamic algorithms. In the previous section we showed how the relative performance of the algorithms remains the same when a uniform error is applied to the runtime constraints. In that case, the dynamic algorithms adapted to the error by rearranging the schedule to accomplish the same amount of work given the same deadline and budget. In this case, the dynamic algorithms adapt by performing less work (executing fewer workflows) to remain within the constraints while accounting for the delays. In both cases, the static algorithm completed the same amount of work, but did so by exceeding the constraints.

% \begin{figure}[ht]
%   \centering
%   \includegraphics[width=0.5\textwidth]{delays_scores}
%   \caption{Percentage of high scores achieved by each algorithm on Montage with uniform unsorted ensembles when provisioning delay varies from 0 seconds to 15 minutes.}
%   \label{fig:delays_scores}
% \end{figure}
